The problem and promise of scale in multilayer networks

### 2020-02-03 paper/manuscript.Rmd
reorg figs
Update manuscript.Rmd and manuscript.pdf
social scale results

@@

* increasing layer relevance as more individuals are connected with increasing buffer size
* decrease in connective redundancy due an increase in summer forest degree at the last (500m) social threshold
* increasing graph strength consistent with increasing strength in winter

@@

##
Results and interpretation of temporal scale

Results and interpretation of spatial scale

Results and interpretation of social scale

>>>>

We observed variation in multilayer network metrics as a function of changes in social, spatial, and temporal scale.

In general, individuals in multilayer networks became more connected as a function of social scale, however, this relationship varied by habitat type and season. As social scale increased, connective redundancy increased rapidly when groups were formed based on ~100m threshold, followed by a plateau and slight decrease at higher thresholds, presumably due to an increase in summer forest degree at ~500m (Figure 3b). Regardless of social scale, layer relevance did not change for any habitat types or seasons, which suggests habitat-by-season layers captured most, if not all, of the potential connections and individual would have across all networks (Figure 3c). Finally, somewhat predictably, graph strength for winter networks increased up to ~100-200m thresholds, followed by a plateau, while graph strength for summer networks did not change as the social threshold increased (Figure 3d).

* increasing graph strength consistent with increasing strength in winter

@@

@@
